---
title: "single_cell"
output: pdf_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(Seurat)
library(dplyr)
library(Matrix)

#KS OBJECT ( 7 DAYS KETOROLAC)
load("KS.Robj", verbose=TRUE)


#tSNE
KS <- RunTSNE(object = KS, dims.use = 1:13, do.fast = TRUE)
TSNEPlot(object = KS,do.label=TRUE)


ks.markers <- FindAllMarkers(object = KS , min.pct = 0.25, thresh.use = 0.25)

#heatmap of TOP 5 genes 
top5_ks <- ks.markers %>% group_by(cluster) %>% top_n(5, avg_logFC)
#pdf(file="KS_heatmap_top_5.pdf",width=20,height=20)
DoHeatmap(object = KS, genes.use = top5_ks$gene,  disp.min = -1,
          disp.max = 1 ,slim.col.label = TRUE, remove.key = TRUE, col.low="green",
          col.mid = "black",col.high="red",group.cex = 20,
          group.spacing = 0.15,cex.col = 20,
          cex.row = 25)
#dev.off()


#heatmap of  TOP 10 genes 
top10_ks <- ks.markers %>% group_by(cluster) %>% top_n(10, avg_logFC)
#pdf(file="KS_heatmap_top_10.pdf",width=30,height=30)
DoHeatmap(object = KS, genes.use = top10_ks$gene,  disp.min = -1,
          disp.max = 1 ,slim.col.label = TRUE, remove.key = TRUE, col.low="green",
          col.mid = "black",col.high="red",group.cex = 20,
          group.spacing = 0.15,cex.col = 20,
          cex.row = 25)
#dev.off()


current.cluster.ids <- c(0, 1, 2, 3, 4, 5,6,7,8,9,10)
new.cluster.ids <- c("Bcells/Endothelial","Tcells","Bcells/Granulocytes","Bcells/Granulocytes "," ","Dendritic/Granulocytes","Immune Cells","Dendritic","Macrophages","NK/Tcells","Granulocytes ")
KS@ident <- plyr::mapvalues(x =  KS@ident, from=current.cluster.ids, to = new.cluster.ids)
#pdf(file="KS_tsne.pdf",width=12,height=10)
TSNEPlot(object =  KS, do.label = TRUE, pt.size = 1.5,colors.use=c("gold4","darkgreen","goldenrod3","tan3","snow4","tan4","blue","orange","red","darkseagreen","brown"))
#dev.off()


#Violin plots
#B CELLS
#nams <- c("Cd79a", "Cd79b","Cd19","Blk")
#pdf(paste(nams,"_Bcells_Markers_KS.pdf"))
VlnPlot(object = KS, features.plot = c("Cd79a"))
VlnPlot(object = KS, features.plot = c("Cd79b"))
VlnPlot(object = KS, features.plot = c("Cd19"))
VlnPlot(object = KS, features.plot = c("Blk"))
#dev.off()

#Featureplot
#B cells
#pdf(file="KS_Bcells.pdf",width=10,height=10)
FeaturePlot(object =KS, features.plot = c("Cd79a","Cd79b","Cd19","Blk"), cols.use = c("grey", "blue"), reduction.use = "tsne")
#dev.off()





#Macrophages
#nams <- c("Adgre1","Cd163","Cd14","Csf1r","Ccr2")
#pdf(paste(nams,"_Macrophages_Markers_KS.pdf"))
VlnPlot(object = KS, features.plot = c("Adgre1"))
VlnPlot(object = KS, features.plot = c("Cd163"))
VlnPlot(object = KS, features.plot = c("Cd14"))
VlnPlot(object = KS, features.plot = c("Csf1r"))
VlnPlot(object = KS, features.plot = c("Ccr2"))
#dev.off()

#pdf(file="KS_Macrophages.pdf",width=10,height=10)
FeaturePlot(object =KS, features.plot = c("Adgre1","Cd163","Cd14","Csf1r","Ccr2"), cols.use = c("grey", "blue"), reduction.use = "tsne")
#dev.off()



#Mast cells
#nams <- c("Kit")
#pdf(paste(nams,"_Mast_Markers_KS.pdf"))
#VlnPlot(object = KS, features.plot = c("Fcer1a"))
VlnPlot(object = KS, features.plot = c("Kit"))
#VlnPlot(object =KS, features.plot = c("Tpsab1"))
#dev.off()


#pdf(file="KS_Mast.pdf",width=10,height=10)
FeaturePlot(object =KS, features.plot = c("Kit"), cols.use = c("grey", "blue"), reduction.use = "tsne")
#dev.off()


#Neutrophil
#nams <- c("Gsr")
#pdf(paste(nams,"_Neutrophils_Markers_KS.pdf"))
VlnPlot(object = KS, features.plot = c("Gsr"))
#dev.off()


#pdf(file="KS_Neutrophil.pdf",width=10,height=10)
FeaturePlot(object =KS, features.plot = c("Gsr"), cols.use = c("grey", "blue"), reduction.use = "tsne")
#dev.off()





#T cells
#nams <- c("Cd3d","Cd3e","Cd3g","Cd247")
#pdf(paste(nams,"_Tcells_other_Markers_KS.pdf"))
VlnPlot(object = KS, features.plot = c("Cd3d"))
VlnPlot(object = KS, features.plot = c("Cd3e"))
VlnPlot(object = KS, features.plot = c("Cd3g"))
VlnPlot(object = KS, features.plot = c("Cd247"))
#dev.off()

#pdf(file="KS_Tcell_other_markers.pdf",width=10,height=10)
FeaturePlot(object =KS, features.plot = c("Cd3d","Cd3e","Cd3g","Cd247"), cols.use = c("grey", "blue"), reduction.use = "tsne")
#dev.off()






